The \dealii{} Library, Version 9.3

### 2021-06-22 9.3/paper.tex
Numerous minor changes

Additionally, the particle infrastructure now supports a faster search algorithm
for particles that moved farther than one cell width between particle sorting
operations, and support for updating ghost particles (particles that live in
ghost cells around the local domain) by updating their properties instead of
destroying and rebuilding their container. The latter step improves the
efficiency of ghost particle exchange significantly. With this feature,
\dealii can be used for scalable parallel Lagrangian
models such as the Discrete Element Method (DEM) \cite{golshan2021lethedem}
or Molecular Dynamics.

@@

These new multigrid variants promise fewer solver
iterations and better parallel scalability than the existing local
smoothing algorithms, but have to deal with
hanging nodes within each level and general require more computational
work per iteration overall.

The transfer operators between two levels have been implemented in the new class \texttt{MGTwoLevel\allowbreak Transfer}, which can be set up via the functions \texttt{MGTwoLevel\allowbreak Transfer::\allowbreak reinit\_\allowbreak geometric\_\allowbreak transfer()} or \texttt{MGTwo\allowbreak LevelTransfer::\allowbreak reinit\_\allowbreak polynomial\_\allowbreak transfer()} for given
\texttt{DoFHandler} and \texttt{AffineConstraints} objects
corresponding to the two levels. The resulting transfer operators
can then be collected in a single
\texttt{MGTransfer\allowbreak GlobalCoarsening} object that can be used just as the previous workhorse \texttt{MGTransferMatrixFree} within the \texttt{Multigrid}
algorithm.
%Several common operations are encoded in utility
%functions in the \texttt{MGTransferGlobalCoarseningTools}
%namespace.
To facilitate the construction of matrix diagonals with matrix-free methods as well as a matrix representation of the coarse level matrix, new utility functions \texttt{create\_diagonal()} and \texttt{create\_matrix()} from
the \texttt{MatrixFreeTools} namespace have been added (see also Subsection~\ref{subsec:mf}).

@@

In the case that even higher polynomial degrees are needed, one can precompile the
relevant internal classes
(\texttt{FEEvaluationFactory}, \texttt{FEFaceEvaluationFactory}, \texttt{CellwiseInverseMassFactory}) in the user code for needed \texttt{degree}s
and \texttt{VectorizedArrayType}s in the following way:
\begin{c++}
#define FE_EVAL_FACTORY_DEGREE_MAX 12

@@

\item \texttt{step-66} shows how to solve a nonlinear problem using Newton's method in the matrix-free
framework in parallel. The PDE considered is the Gelfand problem $-\triangle u = \exp(u)$.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
within the \texttt{MeshWorker::mesh\_loop()} framework. This tutorial demonstrates a
simple to assemble face integrals.

\item \texttt{step-75} demonstrates a state-of-the-art way of solving a simple
      Laplace problem using $hp$-adaptation and hybrid multigrid methods on machines
      with distributed memory. This tutorial points out particularities in porting
      serial $hp$-adaptive code for parallelization. Furthermore, it guides through
      the process of writing an efficient preconditioner for $hp$-adaptive applications.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Michele Bucelli,
Marcus Calhoun-Lopez,
Fabian Castelli, %He provided major contributions to candi for v9.3
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan.

>>>>

Additionally, the particle infrastructure now supports a faster search algorithm
for particles that moved farther than one cell width between particle sorting
operations, and support for updating ghost particles (particles that live in
ghost cells around the local domain) by updating their properties instead of
destroying and rebuilding their container has been added. The latter step improves the
efficiency of ghost particle exchange significantly. With this feature,
\dealii can be used for scalable parallel Lagrangian
models such as the Discrete Element Method (DEM) \cite{golshan2021lethedem}
or Molecular Dynamics.

@@

These new multigrid variants promise fewer solver
iterations and better parallel scalability than the existing local
smoothing algorithms, but have to deal with
hanging nodes within each level and generally require more computational
work per iteration overall.

The transfer operators between two levels have been implemented in the new class \texttt{MGTwoLevel\allowbreak Transfer}, which can be set up via the functions \texttt{MGTwoLevel\allowbreak Transfer::\allowbreak reinit\_\allowbreak geometric\_\allowbreak transfer()} or \texttt{MGTwo\allowbreak LevelTransfer::\allowbreak reinit\_\allowbreak polynomial\_\allowbreak transfer()} for given
\texttt{DoFHandler} and \texttt{AffineConstraints} objects
corresponding to the two levels. The resulting transfer operators
can then be collected in a single
\texttt{MGTransfer\allowbreak GlobalCoarsening} object that can be used just as the previous workhorse \texttt{MGTransferMatrixFree} within the \texttt{Multigrid}
algorithm.
%Several common operations are encoded in utility
%functions in the \texttt{MGTransferGlobalCoarseningTools}
%namespace.
To facilitate the construction of matrix diagonals with matrix-free methods as well as a matrix representation of the coarse level matrix, new utility functions \texttt{create\_diagonal()} and \texttt{create\_matrix()} have been added to
the \texttt{MatrixFreeTools} namespace (see also Subsection~\ref{subsec:mf}).

@@

In the case that even higher polynomial degrees are needed (e.g., $k\le 12$), one can precompile the
relevant internal classes
(\texttt{FEEvaluationFactory}, \texttt{FEFaceEvaluationFactory}, \texttt{CellwiseInverse\allowbreak MassFactory}) in the user code for needed \texttt{degree}s
and \texttt{VectorizedArrayType}s in the following way:
\begin{c++}
#define FE_EVAL_FACTORY_DEGREE_MAX 12

@@

\item \texttt{step-66}, a program written by Fabian Castelli at Karlsruhe Institute of Technology, shows how to solve a nonlinear problem using Newton's method in the matrix-free
framework in parallel. The PDE considered is the Gelfand problem $-\triangle u = \exp(u)$.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
within the \texttt{MeshWorker::mesh\_loop()} framework. This tutorial demonstrates a
simple way to assemble face integrals.

\item \texttt{step-75} demonstrates a state-of-the-art way of solving a simple
      Laplace problem using $hp$-adaptation and hybrid multigrid methods on machines
      with distributed memory. This tutorial points out particularities in porting
      serial $hp$-adaptive code for parallelization. Furthermore, it guides through
      the process of writing an efficient matrix-free preconditioner for $hp$-adaptive applications.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Michele Bucelli,
Marcus Calhoun-Lopez,
Fabian Castelli, %He provided major contributions to candi for v9.3
Praveen Chandrashekar,
Conrad Clevenger,
Fabian Castelli,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Benjamin Uekermann,
Peter Westerbaan.
